Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-01-19 manuscript/HIAs.qmd
arrange municipality plot and outline

# Make map to show where the three municipalities are
#
#

@@

outline2 <- outline |>
  st_intersection(muni3)

ocean <- muni3 |>
  st_difference(outline)

tm_shape(muni3)+
    tm_borders()+
  tm_facets(by = "Municipality")+
  tm_shape(outline2)+
    tm_fill(col = "lightgreen",
             alpha=.4)+
  tm_shape(ocean)+
    tm_polygons(col = "lightblue",
                border.col = "black",
            alpha=1)+
  #tm_shape(muni3)+
  #  tm_borders()+
  tm_shape(dk)+
    tm_polygons(col = "grey",
                alpha=.8)+
  tm_shape(nature3)+
  tm_polygons(col = "red",
              border.col = "red",
              lwd=3)

>>>>

# Make map to show where the three municipalities are
# First, get centroids
centroids <- muni3 |>
  st_centroid()

positionMap <- tm_shape(outline)+
  tm_polygons() +
  tm_shape(centroids)+
    tm_text(text = "Municipality",
      size = 1,
      xmod = 2,
      ymod=-1)+
  tm_symbols(size = 2,
             shape = 17,
             col="black")+
  tm_grid(projection = 4326)+
  tm_layout(bg.color = "skyblue")

@@

# Simplified coastline
outline2 <- outline |>
  st_intersection(muni3)

# Polygons for the oceans in each municipality
ocean <- muni3 |>
  st_difference(outline)

# Plot (could perhaps add the EDM here as well)
muniPlot <- tm_shape(muni3)+
    tm_borders()+
  tm_facets(by = "Municipality",
            ncol=2)+
  tm_shape(outline2)+
    tm_fill(col = "lightgreen",
             alpha=.4)+
  tm_shape(ocean)+
    tm_polygons(col = "skyblue",
                border.col = "black")+
  tm_shape(dk)+
    tm_polygons(col = "grey",
                alpha=.8)+
  tm_shape(nature3)+
  tm_polygons(col = "red",
              border.col = "red",
              lwd=3)

tmap_arrange(positionMap, muniPlot,
             widths = c(.4, .6))
```
